Redshift evolution of the SN stretch distribution

### 2019-10-14 Nicolas.tex
First draft sec:sam

\section{Sample}
We use data from 5 different surveys, 3 of which had selection effects that we
tried to remove with a statistical approach in lack of precise data concerning
the instruments' capacity to acquire fluxes. Here it is:

>>>>

\section{Sample}\label{sec:sam}

We use data from 5 different surveys: Hubble Space Telescope (HST, REF),
Supernova Nearby Factory (SNf, REF), Supernova Legacy Survey (SNLS, Aster 2006,
Betoule 2014), Sloan DSS (SDSS, REF) and Panstarr-1 (PS1, REF). The last 3 had
selection effects that come from the "brighter-slower" and "brighter-bluer"
relations: the first SNe Ia that are missed by the instruments are the redder
and faster ones. That implies that taking all of these surveys' data would not
represent the stretch distribution that Nature could give us.

As such, we determined the maximum redshift at which we would cut these samples
to get complete ones. We used a statistical approach in lack of precise data
concerning the instruments' capacity to acquire fluxes. We proceeded by making
histograms of the surveys, and defining a function of the expected SNe Ia rate:
\begin{center}
    $ \displaystyle N\St{SNe Ia} = a \times V\z$
\end{center}
with $a$ the density of SNe Ia and $V\z$ the volume of Universe in each bin.
Before selection effects, the histograms are supposed to grow proportionnaly to
$V\z$ assuming an homogeneous repartition of SNe Ia. When we start to miss some
supernovae, this growth is not followed anymore.

To determine this limit, we first took the observed counts in each bin of the
histograms. We then fitted $a$ on these counts for different numbers of bins
used to fit: the quality of the fit diminishes when we use bins that include
selection effects. To quantize this, we computed the expected counts from the
fitted $a$ in the same bins we used for the observed counts. That allowed us to
compute the poissonian probability in each bin, given by
\begin{center}
    $ \displaystyle p(k) = \frac{\lambda^k}{k!}e^{-\lambda}$
\end{center}
with $k$ the expected counts, $\lambda$ the observed counts. This work is done 100
times with a random number of total bins, $a$ being fitted 4 times on a
different and random number of bins used to fit each time. We interpolate these
400 poissonian evolutions to get one final result that is as close as possible
to accurately represent how the probability to follow the expected rate evolves.

To get the maximum redshift after which we stop following the expected rate, we
took the redshift for which we are at a 0.3 on the interpolated cumulative
distribution function. We chose that value to have a systematic analytical
result that matches what we expect from the histograms; its impact on the work
after is to be studied.

\begin{table}[htbp!]
    \centering
    \caption{Number of SNe Ia effectively used for each survey.}
    \label{tab:sample}
    \begin{tabularx}{\linewidth}{|Y*{1}{|Y}|}\hline
        \rowcolor{gray!15} Survey & Number of SNe Ia \\\hline\hline
        SNf & 141 \\\hline
        PS1 & 178 \\\hline
        SDSS & 206 \\\hline
        SNLS & 138 \\\hline
        HST & 26 \\\hline
    \end{tabularx}
\end{table}

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=\linewidth]{Article_figures/zmax_determination.pdf}
    \caption{$z\St{max}$ determination from the interpolated poissonian
    evolutions.}
    \label{fig:zdet}
\end{figure}

\begin{figure}[htbp!]
    \centering
    \includegraphics[width=\linewidth]{Article_figures/surveys_cuts_x.pdf}
    \caption{SDSS, SNLS and PS1 samples cut at $z\St{max}$ as explained in
    section \ref{sec:sam}. The data we use is in plain markers.}
    \label{fig:surveys_cuts}
\end{figure}
